Binary companions of red giant stars in \apogee\ \DR

### 2018-02-27 paper/1-catalog/twoface-catalog.tex
Residuals figure

However, there are a number of caveats to keep in mind about this estimate of
the excess variance distribution.
First, we do not remove triple or other multiple systems: For any individual
system, the radial velocity variations induced by other massive bodies will lead
to larger preferred values for the excess variance parameter.
We don't expect there to be a large number of triple systems in our sample, but
this is still an important consideration for future efforts.
Second, we are sensitive to outliers and very non-Gaussian systematic error
distributions.
In fact, the residuals we find away from our best-fit two-body orbital solutions
do not appear strictly Gaussian and have tails towards larger systematic errors.
\figurename~\ref{fig:residuals} shows the distribution of normalized residuals,
$R_{nk}$, for each visit: the $k$ visit velocities for each $n$ star, $v_{nk}$,
minus the predicted radial velocity from the best-fitting sample returned by
\thejoker, $\hat{v}^*_{nk}$, normalized by the excess-variance-included
uncertainty, $\sigma_{nk}^* = \sqrt{\sigma_{nk}^2 + \hat{s}_{n}^2}$, where
$\hat{s}_{n}$ is computed from the excess-variance parameter of the best-fitting
sample:
\begin{equation}
    R_{nk} = \frac{v_{nk} - \hat{v}^*_{nk}}{\sqrt{\sigma_{nk}^2 +
    \hat{s}_{n}^2}} \quad .
\end{equation}

@@

% Notebook: "Residuals-vs-metadata"
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{residuals}
% \end{center}
% \caption{%
% \todo{stuff}
% \label{fig:residuals}
% }
% \end{figure}

@@

@@

>>>>

However, there are a number of caveats to keep in mind about this estimate of
the excess variance distribution.
First, we do not remove triple or other multiple systems: For any individual
system, the radial velocity variations induced by other massive bodies will lead
to larger preferred values for the excess variance parameter.
We don't expect there to be a large number of triple systems in our sample, but
this is still an important consideration for future efforts.
Second, we are sensitive to outliers and very non-Gaussian systematic error
distributions.
We later assess the non-Gaussianity of the visit velocity uncertainties by
looking at the visit velocity residuals away from the orbit samples produced by
\thejoker\ using the updated excess variance distribution (see
\sectionname~\ref{sec:discuss-assumptions}).

@@

@@

\subsection{Assumptions}
\label{sec:discuss-assumptions}

@@

We find that the residuals away from our best-fit two-body orbital solutions
appear close to Gaussian, indicating that the \emph{simple noise model}
assumption may be sufficient.
\figurename~\ref{fig:residuals} shows the distribution of normalized residuals,
$R_{nk}$, for each visit: the $k$ visit velocities for each $n$ star, $v_{nk}$,
minus the predicted radial velocity from the best-fitting sample returned by
\thejoker, $\hat{v}^*_{nk}$, normalized by the excess-variance-included
uncertainty, $\sigma_{nk}^* = \sqrt{\sigma_{nk}^2 + \hat{s}_{n}^2}$, where
$\hat{s}_{n}$ is computed from the excess-variance parameter of the best-fitting
sample:
\begin{equation}
    R_{nk} = \frac{v_{nk} - \hat{v}^*_{nk}}{\sqrt{\sigma_{nk}^2 +
    \hat{s}_{n}^2}} \quad . \label{eq:normresid}
\end{equation}

% Notebook: "Residuals-vs-metadata"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{residuals}
\end{center}
\caption{%
Histogram shows the distribution of normalized visit residuals (see
\eqname~\ref{eq:normresid}) for all \nvisits\ used in the final run of
\thejoker\ (i.e. with updated excess variance distribution parameters inferred
in \sectionname~\ref{sec:inferjitter}).
The orange curve shows that expected for Gaussian uncertainties.
The distribution appears mostly Gaussian over a large range of residual values,
with slightly more populated tails and evidence of a few catastrophic outliers.
\label{fig:residuals}
}
\end{figure}
